\large{Vipassana for Hackers} \\ \Huge{Paper Three: Why Meditate?} \\ \large\textit{Version 0.1}

### 2023-06-01 paper-three/paper-three.tex
FIX: get paper three rendering again (Linux)

\documentclass[a4paper, amsfonts, amssymb, amsmath, reprint, showkeys, nofootinbib, twoside]{revtex4-1}

@@

\title{%
  \large{Vipassana for Hackers} \\
  \Huge{Paper Three: Why Meditate?} \\
  \large\textit{Version 0.1}
}
\author{Steven Deobald}
\email[Correspondence email address: ]{steven@deobald.ca}
\affiliation{www.vipassana-for-hackers.org}
\date{\today}

@@

It is important to understand this point as it underpins all other aspects of the
technique of Vipassana. Someone who is learning Vipassana need not accept this
principle as fact. Rather, a 10-day Vipassana course is a sort of laboratory where the
principle can be tested and experienced for oneself.

@@

\begin{itemize}
  \item reset frame of reference outside oneself, outside one's own lifetime: ``trees
    for god'' and obvious karma (sidu/booga smoking)
  \item Time: Nat Friedman's blog post?
  \item bible; ``a perfect set of rules''; nature itself <=> perception; ``perfect
    perception (vision)''; inner perception (sensation mirror) --- harris v. peterson
  \item clarification: ``isn't that what makes us human?'' (emotions) --- rather,
    what makes us animal
  \item ``How to Change Your Mind'' --- ego dissolution --- specific advantages?
  \item seeing oneself as aggregate and the path from singular => aggregate
    (neuroscience behind hemispheres)
\end{itemize}

>>>>

\documentclass[a4paper, amsfonts, amssymb, amsmath, reprint, showkeys, nofootinbib, twoside]{revtex4-2}

@@

\title{
  \large{Vipassana for Hackers} \\
  \Huge{Paper Three: Why Meditate?} \\
  \large\textit{Version 0.1}
}
\author{Steven Deobald}
\email[Correspondence email address: ]{steven@deobald.ca}
\affiliation{www.vipassana-for-hackers.org}
\date{\today}

@@

It is important to understand this point as it underpins all other aspects of the
technique of Vipassana. Someone who is learning Vipassana need not accept this
principle as fact. Rather, a 10-day Vipassana course is a sort of laboratory where the
principle can be tested and experienced directly.

@@

\begin{itemize}
  \item reset frame of reference outside oneself, outside one's own lifetime: ``trees
    for god'' and obvious karma (sidu/booga smoking)
  \item Time: Nat Friedman's blog post?
  \item Is it really possible? https://twitter.com/ID\_AA\_Carmack/status/1260698271422570497
    The “speed of thought” (neuron conduction speed) is only 110m/s, which isn’t that fast. 9 ms of latency just in your arm!
    https://www.youtube.com/watch?v=MeHoU-arXgY
  \item bible; ``a perfect set of rules''; nature itself <=> perception; ``perfect
    perception (vision)''; inner perception (sensation mirror) --- harris v. peterson
  \item clarification: ``isn't that what makes us human?'' (emotions) --- rather,
    what makes us animal
  \item ``How to Change Your Mind'' --- ego dissolution --- specific advantages?
  \item seeing oneself as aggregate and the path from singular => aggregate
    (neuroscience behind hemispheres)
\end{itemize}
